Comparing rule sets across environments

### 2023-05-31 EnvironmentalData/CrossEnvironmentComparisons/comparing_rule_sets_across_environments.Rmd
Updating proportion of viral sequences Fig 8.

```{r}
env_path <- '/Users/riddellj/Documents/Research/VSTE/VSTE_Old_Pull/EnvironmentalData/'
viruses_tara <- read_csv(paste(env_path, "tara_num_viruses.csv", sep=""))
viruses_tara$environment <- "global_oceans"
viruses_le <- read_csv(paste(env_path, "le_num_viruses.csv", sep=""))
viruses_le$environment <- "Lake_Erie"
viruses_lm <- read_csv(paste(env_path, "lake_michigan_num_viruses.csv", sep=""))
viruses_lm$environment <- "Lake_Michigan"
viruses_ww <- read_csv(paste(env_path, "wastewater_num_viruses.csv", sep=""))
viruses_ww$environment <- "wastewater"
viruses_dw <- read_csv(paste(env_path, "drinking_water_uknl_num_viruses.csv", sep=""))

viruses_rest <- rbind(viruses_tara, viruses_le, viruses_lm, viruses_ww)
write.csv(viruses_rest, 'env_rest_num_viruses.csv')
```

@@

viruses_all <- rbind(viruses_dw, viruses_rest)
```

@@

>>>>

```{r}
env_path <- '/Users/riddellj/Documents/Research/VSTE/VSTE_Old_Pull/EnvironmentalData/'
viruses_tara <- read_csv(paste(env_path, "tara_num_viruses.csv", sep=""))
viruses_tara$environment <- "global_oceans"
viruses_le <- read_csv(paste(env_path, "le_num_viruses.csv", sep=""))
viruses_le$environment <- "Lake_Erie"
viruses_lm <- read_csv(paste(env_path, "lake_michigan_num_viruses.csv", sep=""))
viruses_lm$environment <- "Lake_Michigan"
viruses_ww <- read_csv(paste(env_path, "wastewater_num_viruses.csv", sep=""))
viruses_ww$environment <- "wastewater"
viruses_dw <- read_csv(paste(env_path, "drinking_water_uknl_num_viruses.csv", sep=""))
#viruses_dw <- read_csv("../DrinkingWaterMetagenomes/drinking_water_num_viruses.csv")

viruses_rest <- rbind(viruses_tara, viruses_le, viruses_lm, viruses_ww)
write.csv(viruses_rest, 'env_rest_num_viruses.csv')
#viruses_rest <- read.csv('env_rest_num_viruses.csv')

```

@@

viruses_all <- rbind(viruses_dw, viruses_rest)
#viruses_all <- rbind(viruses_dw, viruses_rest[-1])

```

@@

# simplified version comparing rulesets based on their accuracy type

```{r}
viruses_all$ruletype <- viruses_all$best_coloring
viruses_all$ruletype[viruses_all$best_coloring=="VS2 combo"] <- "high MCC"

fig <- ggplot(viruses_all, aes(x=ruletype, y=prop_vir, 
                                  color=ruletype, fill=ruletype)) +
  geom_boxplot() +
  #geom_point() +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=10),
    axis.text.x=element_text(size=12, angle = 90, vjust = -0.1),
    legend.text=element_text(size=12),
    axis.title=element_text(size=12),
    strip.background = element_rect(fill="white", color="grey"),
    strip.text = element_text(color="black", size=12)
  ) +
  xlab("Environment") +
  ylab("Proportion of Contigs >3kb Viral") +
  scale_fill_manual(name="",
                     values = alpha(c(rev(magma(7)[3:6]), "grey"), 0.4)) +
  scale_color_manual(name="",
                     values = alpha(c(rev(magma(7)[3:6]), "grey"), 0.6)) +
  facet_wrap(~environment2)
fig

ggsave(
  "simplified_environmental.png",
  plot = fig,
  scale = 1,
  width = 6.5,
  height = 4,
  units = c("in"),
  dpi = 300,
  limitsize = TRUE
)
```
